---
title: "Introduction to the geoops package"
author: "Scott Chamberlain"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
vignette: >
  %\VignetteIndexEntry{Introduction to the geoops package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

`geoops` is an R package.

## Install

If installing `leaflet`

```{r eval=FALSE}
install.packages("leaflet")
```

from Github

```{r eval=FALSE}
devtools::install_github("ropenscilabs/geoops")
```

```{r}
library("geoops")
```

## get json c++ library version info

```{r}
geoops::version()
```

## distance

Calculate distance between two GeoJSON points

```{r}
pt1 <- '{
  "type": "Feature",
  "properties": {
    "marker-color": "#f00"
   },
   "geometry": {
      "type": "Point",
      "coordinates": [-75.343, 39.984]
   }
}'
#'
pt2 <- '{
  "type": "Feature",
  "properties": {
     "marker-color": "#0f0"
   },
   "geometry": {
      "type": "Point",
      "coordinates": [-75.534, 39.123]
    }
}'
```

```{r}
geo_distance(pt1, pt2)
```

## bearing

Calculate bearing between two points

```{r}
geo_bearing(pt1, pt2)
```

## destination

```{r}
geo_destination(pt1, 50, 90, 'miles')
```

## line distance

Calculate length of GeoJSON LineString or Polygon

```{r}
line <- '{
  "type": "Feature",
  "properties": {},
  "geometry": {
    "type": "LineString",
    "coordinates": [
      [-77.031669, 38.878605],
      [-77.029609, 38.881946],
      [-77.020339, 38.884084],
      [-77.025661, 38.885821],
      [-77.021884, 38.889563],
      [-77.019824, 38.892368]
    ]
  }
}'
geo_line_distance(line, units = "kilometers")
```

## nearest

Calculate nearest point to a reference point

```{r}
point1 <- '{
  "type": "Feature",
  "properties": {
     "marker-color": "#0f0"
   },
  "geometry": {
     "type": "Point",
     "coordinates": [28.965797, 41.010086]
  }
}'
#'
points <- '{
  "type": "FeatureCollection",
  "features": [
    {
      "type": "Feature",
      "properties": {},
      "geometry": {
        "type": "Point",
        "coordinates": [28.973865, 41.011122]
      }
    }, {
      "type": "Feature",
      "properties": {},
      "geometry": {
        "type": "Point",
        "coordinates": [28.948459, 41.024204]
      }
    }, {
      "type": "Feature",
      "properties": {},
      "geometry": {
        "type": "Point",
        "coordinates": [28.938674, 41.013324]
      }
    }
  ]
}'
geo_nearest(point1, points)
```

## Example use case

Get some GeoJSON data, a FeatureCollection of Polygons

```{r}
file <- system.file("examples/zillow_or.geojson", package = "geoops")
x <- paste0(readLines(file), collapse = "")
```

Break each polygon into separate JSON string

```{r}
library("jqr")
polys <- unclass(jq(x, ".features[]"))
```

Using `geo_area`, calculate the area of the polygon

```{r}
areas <- vapply(polys, geo_area, 1, USE.NAMES = FALSE)
```

Visualize area of the polygons as a histogram

```{r}
hist(areas, main = "")
```

Visualize some of the polygons, all of them

```{r}
library(leaflet)
leaflet() %>% 
  addTiles() %>% 
  addGeoJSON(geojson = x) %>% 
  setView(lng = -123, lat = 45, zoom = 7)
```

Just one of them

```{r}
leaflet() %>% 
  addTiles() %>% 
  addGeoJSON(geojson = polys[1]) %>% 
  setView(lng = -122.7, lat = 45.48, zoom = 13)
```

